Early Observations of the Type Ia Supernova \abc:\\ XXX NEED SOMETHING CLEVER TO SAY HERE XXX

### 2017-08-07 doc/ms.tex
Include bolometric calculation from Suhail in the paper.

@@

>>>>

\author{S.~Dhawan}
\affil{European Southern Observatory, Karl-Schwarzschild-Strasse 2, D-85748 Garching bei München, Germany}
\affil{Excellence Cluster Universe, Technische Universität München, Boltzmannstrasse 2, D-85748, Garching, Germany}
\affil{Physik Department, Technische Universität München, James-Franck-Strasse 1, D-85748 Garching bei München, Germany}
\affil{The Oskar Klein Centre, Department of Physics, AlbaNova, SE-106 91 Stockholm, Sweden}

@@

We measure the (pseudo)bolometric luminosity of \abc\ at peak via trapezoidal integration of the reddening-corrected flux from the UV, optical, and NIR (UVOIR) filters. The light curves in the individual filters are interpolated so that $L_\mathrm{bol}$ is evaluated at common epochs in each filter. From this integration, we determine that the maximum UVOIR luminosity of \abc\ is $L_\mathrm{max} = 1.2 \pm 0.1 \times 10^{43} \; \mathrm{erg \; s}^{-1}$. This value is consistent with the sample of normal SNe Ia studied in  \citet{2016A&A...588A..84D}, a sample which excludes low-luminosity SNe.
